Article Title

### 2013-09-25 sections/Results.tex
minor

\subsection*{Data acquisition}
We recorded the calcium activity  of dense populations of neurons in the supragranular layers of mouse primary visual cortex using fast random-access 3D scanning two-photon microscopy \cite{Stosiek:2003,Reddy:2005}   while presenting numerious repetitions of full-field drifting gratings (Fig. 1A and 1B). This technique allowed recording from a large number (150--350) of cells in a small volume of cortical tissue (200 x 200 x 100 $\mu$m) in layers 2/3 and 4. Somatic calcium signals were deconvolved using  sparse nonnegative deconvolution \cite{Vogelstein:2010} (Fig. 1C and 1D).  The average stimulus response was subtracted to remove stimulus covariance and the sample noise covariance matrix was computed (Fig. 1E).

\subsection*{Covariance estimation}
We aim to estimate the true covariance matrix $\Sigma = \mathbb E [(x-\mu)(x-\mu)^\T]$ , where $\mathbb E[\cdot]$ denotes expectation, $x$ denotes the $p\times 1$ vector of real-valued instanteous firing rates of $p$ neurons in a bin of duration $\Delta t$ and $\mu = \mathbb E[x]$.  For more rigourous notation, definitions, and derivations, see Appendix.

>>>>

\subsection*{Data acquisition}
We recorded the calcium activity  of dense populations of neurons in the supragranular layers of mouse primary visual cortex using fast random-access 3D scanning two-photon microscopy \cite{Stosiek:2003,Reddy:2005}   while presenting numerious repetitions of full-field drifting gratings (Fig. 1A and 1B). This technique allowed recording from a large number (150--350) of cells in a small volume of cortical tissue ($200\times200\times100$ $\mu$m$^3$) in layers 2/3 and 4. Somatic calcium signals were deconvolved using  sparse nonnegative deconvolution \cite{Vogelstein:2010} (Fig. 1C and 1D).  The average stimulus response was subtracted to remove stimulus covariance and the sample noise covariance matrix was computed (Fig. 1E).

\input{sections/Figure1.tex}

\subsection*{Covariance estimation}
We aim to estimate the true covariance matrix $\Sigma = \mathbb E [(x-\mu)(x-\mu)^\T]$ , where $\mathbb E[\cdot]$ denotes expectation \TODO{under the true model}, $x$ denotes the $p\times 1$ vector of real-valued instanteous firing rates of $p$ neurons in a bin of duration $\Delta t$ and $\mu = \mathbb E[x]$.  For more rigourous notation, definitions, and derivations, see Appendix.
